Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-02-21 Ben_Manuscripts/transport/Outline.tex
Updates to outline

  Water molecules also exhibit hop diffusion.

  The overwhelming number of water molecules reduces

  Even in the center of the pore, where the density of water molecules is
  highest, individual water molecules exhibit hop diffusion as they create a
  tight hydrogen bond network.
  %TODO: the following is a hypothesis
  \begin{itemize}
	\item Water sticks to pore walls
	\item Dwell times are short
	\item Water tumbles across pore for a while until it sticks again. 
	\item Water gets caught in h-bonds with other water molecules away
	from pore center.
  \end{itemize}

  In this confined environment, the diffusion constant is x times lower than
  expected bulk diffusion coefficient of tip3p water.

  %TODO: study diffusion mechanism of water

@@

  Once again, the trends in the MSD can in large part be explained by the solutes'
  preference for water.
  \begin{itemize}
  	\item Urea, Acetic Acid and Acetamide are all capable of donating hydrogen bonds,
  	while acetone is the first instance of a molecule in this study that can only
  	accept hydrogen bonds. It follows that acetone has the slowest MSD of this grouping.
  	\item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
  	\item Hence, Acetic Acid donates the greatest number of hydrogen bonds and has
  	the highest density throughout the pore region.
  	\item With two nitrogen groups that hydrogen bond relatively infrequently, one might 
  	expect Urea to exhibit much faster transport, however its MSD is comparable to
  	the much stickier acetic acid. 
  	\item Urea is highly soluble in water but not miscible in all proportions like 
  	acetic acid or even acetone.
  	\item Relative to acetic acid, acetamide, urea and acetone spend more time in the head group region.
  	\item There is a large peak near the head groups, but \% of the urea molecules 
  	are behind in the head group region.
  	\item The structure of acetamide differs from acetic acid only by an amine group in place
  	of a hydroxyl group.
  	\item The weaker hydrogen bonding capability of acetamide and an extra nonpolar methyl group compared to
  	Urea makes acetamide even more likely to partition. 
  	\item Urea has two hydrogen bond donor nitrogen atoms. It is not surprising that
  	its density is high near the pore center, particularly near the monomer head groups.

  	\item Acetamide has only one nitrogen atom. One of two peaks in its density is 
  	located close to the peak of Urea, likely corresponding to hydrogen bonds with head groups.
  	A second peak is located within the head group region. %BJC: hbonds with ethers vs. head groups. Or is it just planarity?
  	\item Acetic acid, a carboxylic acid shows a relatively high density in the pore region, with 
  	a peak close to the carboxylate groups.  %BJC: hbonds a lot 
  	\item Acetone is stabilized by accepting hydrogen bonds from water in the pore region, but
    its low polarity and planar shape gives it comparable stability when trapped between head groups.
%  	\item Acetone's has two prominent peaks in its radial density. One is in the pore region and the o
%  	other is relatively deep in the head group region.
  \end{itemize}

@@

  We studied the transport properties of sulfur analogs of glycerol, ethylene glycol 
  and acetone.
%  Finally, we studied the transport properties of sulfur-containing compounds similar
%  to some of the solutes studied above.
  \begin{itemize}
    \item We replaced all but one oxygen atom of ethylene glycol and glycerol with sulfur atoms
    to create Dimercaptoethanol and 2,3-Dimercapto-1-propanol.
    \item We replaced the carbonyl carbon of acetone with sulfur in order to create DMSO. 
  	\item Sulfur is unable to hydrogen bond, however it is soluble in water  %BJC: maybe a reference to why sulfur can't hbond
  	\item Comparisons of their RDFs are shown in Figure~\ref{fig:sulfur_analog_rdfs}.
  \end{itemize}

@@

  \noindent Mercaptoethanol has a similar average RDF and MSD to ethylene glycol.
  \begin{itemize}
    \item There is a much larger uncertainty associated with mercaptoethanol's MSD.
    \item It spends more time in the tail region than ethylene glycol, where transport
    is inherently slower, and may contribute to some slower MSDs.  % Can quantify as a percentage
    \item Conversely, Mercaptoethanol also exhibits some of the highest single solute MSDs % BJC: hypothesis about observation. Remains to be quantified
    \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
    % Dwell time as a function of hbonds?
    \item Some of this can be accounted for by the higher density of mercaptoethanol 
    molecules in the head group / tail region. There are nearly 40 \% more mercaptoethanol
    beyond 0.8 nm from the pore center. 
    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
    monomer head group simultaneously,

    \item Less frequent hydrogen bonding and an affinity for the pore region may be
    responsible for these hops.
  \end{itemize}

@@

  \noindent 2,3-Dimercapto-1-propanol exhibits slower transport than glycerol because it spends more time
  near monomer head groups. % BJC: should I give all the solutes nicknames (i.e. their residue names)?
  \begin{itemize}
    \item Glycerol frequently hydrogen bonds with more than one head group at a time.
    % BJC: can probably quantify the following:
    \item It also hydrogen bonds with water molecules which increases its stability in the pore region
    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups so it gravitates
    towards the head group region.
  \end{itemize}

  \noindent DMSO has a comparable MSD to acetone even though its molecular weight is
  about 25 \% larger.
  \begin{itemize}
  	\item The pyramidal structure of DMSO may force it to spend more time closer to
  	the pore center.  % BJC: might be a good place for a numbers comparison
  	\item There are 20 \% more acetone than DMSO molecules in the region beyond 0.8 nm from the pore center.  % based on actual number, not density
  	\item DMSO cannot as easily work its way in and out of the dense head group region. 
  	\item There is a peak in DMSO's radial density near 1.1 nm which may be a consequence of 
  	solute molecules that get stuck in the tails.
%    \item This may be due to the higher polarity and the pyramidal structure of DMSO.
%    \item DMSO is more stable in water than acetone and less stable in the head group region than acetone.
%    \item There is a peak in the DMSO radial density function in the tails which means some of them still
%    find their way back there and get trapped.
  \end{itemize}

@@

%  \subsection*{Transport of Ions} % probably just sodium
%
%  Sodium ions also exhibit hop diffusion because polarized water and
%  carboxylate head groups both work to neutralize its charge.
%  \begin{itemize}
%	\item Ions get trapped in oxygen 'cages' composed of combinations
%	of water molecules, carboxylate head groups and ether oxygens connecting
%	the head groups to their tails.
%  	\item Interesting coordination number data
%	\item Dwell time proportional to surrounding charge within coordination shell
%  \end{itemize}

@@

  Water content affects pore size. Experiments to understand this could be useful.

  Separate polar molecules by creating monomers with more hydrophilic head group components.
  More incentive to dwell on walls.

  Make ions move faster by placing charges in sterically inaccessible places.

@@

  We can use this intuition in order to modify our monomers for a specific 
  separation.
  \begin{itemize}
	\item Increase number of h-bond sites to increase selectivity towards water 
	over polar molecules
	\item Also separate acetone (things with only h-bond accepting groups) in this way
  \end{itemize}

>>>>

  The MSD of water is a weak function of the solute residue disolved in
  the pores.
  \begin{itemize}
  	\item Large molecules like glycerol and ribose obstruct the movement
  	of water molecules forcing them to have lower MSDs
  	\item I don't know why the MSD is fast in the fastest systems or why DMSO is slow.
  	\item Sulfur containing compounds have slowest water transport
  	\item How do 24 solute molecules have such a drastic effect on water motion
  \end{itemize}

  % BJC: MSDs only calculated for water molecules that spend > 95 % of their
  % time in the pore. Pore region / tail region cutoff is at 1.5 nm (approximate location of lowest radial water density) 
  \begin{figure}
  \centering
  \includegraphics[width=\textwidth]{water_msd.pdf}
  \caption{}\label{fig:water_msd}
  \end{figure}

  % BJC. Other Notes:
  % There is no discernable trend in flux of water to/from pores. Most levels stay 
  % comparable to their initial values while a handful have ~50 water molecules that
  % enter the pore during the simulation.
  % Water molecules that spend > 95 % of their time within 1 nm of the pore center 
  % have lower MSDs -- although there aren't a lot of them to average over. They are
  % probably lower because they can't be moving much to stay so confined

@@

  Once again, the trends in the MSD can in large part be explained by the solutes'
  preference for water.
  \begin{itemize}
  	\item Urea, Acetic Acid and Acetamide are all capable of donating hydrogen bonds,
  	while acetone is the first instance of a molecule in this study that can only
  	accept hydrogen bonds. It follows that acetone has the slowest MSD of this grouping.
  	\item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
  	\item Hence, Acetic Acid donates the greatest number of hydrogen bonds and has
  	the highest density throughout the pore region.
  	\item All other solutes show a higher preference for the tail region where three 
  	dimensional confinement directly contributes to a lower MSD.
  	\item Urea likely compensates for its loss of mobility in the head group region by
  	making large hops upon escape into the pore region.
  	\item Urea frequently moves between the head group and pore region because its planar
  	shape makes it easier to transition between regions.% could quantify transition frequency probably. It seems like it might yield something. But also might make things more ambiguous.
  	\item As the solutes become less polar, their MSD decreases. 
  	\item Acetamide has one less amine group than Urea and a corresponding smaller MSD.
  	\item Despite a peak in its density near the pore center due to its water solubility,
  	Acetone is the least polar and spends the most time outside the tail group region 
  	leading to the lowest MSD.
%  	\item With two nitrogen groups that hydrogen bond relatively infrequently, one might 
%  	expect Urea to exhibit much faster transport, however its MSD is comparable to
%  	the much stickier acetic acid. 
%  	\item Urea is highly soluble in water but not miscible in all proportions like 
%  	acetic acid or even acetone.
%  	\item Relative to acetic acid, acetamide, urea and acetone spend more time in the head group region.
%  	\item There is a large peak near the head groups, but \% of the urea molecules 
%  	are behind in the head group region.
%  	\item The structure of acetamide differs from acetic acid only by an amine group in place
%  	of a hydroxyl group.
%  	\item The weaker hydrogen bonding capability of acetamide and an extra nonpolar methyl group compared to
%  	Urea makes acetamide even more likely to partition. 
%  	\item Urea has two hydrogen bond donor nitrogen atoms. It is not surprising that
%  	its density is high near the pore center, particularly near the monomer head groups.
%  	
%  	\item Acetic acid, a carboxylic acid shows a relatively high density in the pore region, with 
%  	a peak close to the carboxylate groups.  %BJC: hbonds a lot 
%  	\item Acetone is stabilized by accepting hydrogen bonds from water in the pore region, but
%    its low polarity and planar shape gives it comparable stability when trapped between head groups.
%  	\item Acetone's has two prominent peaks in its radial density. One is in the pore region and the o
%  	other is relatively deep in the head group region.
  \end{itemize}

@@

  We also studied the transport properties of sulfur analogs of glycerol, ethylene
  glycol and acetone.
%  Finally, we studied the transport properties of sulfur-containing compounds similar
%  to some of the solutes studied above.
  \begin{itemize}
    \item We replaced all but one oxygen atom of ethylene glycol and glycerol with sulfur atoms
    to create Dimercaptoethanol and 2,3-Dimercapto-1-propanol.
    \item We replaced the carbonyl carbon of acetone with sulfur in order to create DMSO. 
  	\item Sulfur is unable to hydrogen bond, however it is soluble in water  %BJC: maybe a reference to why sulfur can't hbond
  	\item Comparisons of their RDFs are shown in Figure~\ref{fig:sulfur_analog_rdfs}.
  \end{itemize}

@@

  \noindent Mercaptoethanol has a similar average RDF and MSD to ethylene glycol.
  \begin{itemize}
    \item There is a much larger uncertainty associated with mercaptoethanol's MSD.
    \item It spends more time in the tail region than ethylene glycol, where transport
    is inherently slower, and may contribute to some slower MSDs.  % Can quantify as a percentage
    \item Conversely, Mercaptoethanol also exhibits some of the highest single solute MSDs  % Only methanol has greater (I think)
    \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
    \item This may lead to larger hops in the pore region.
    \item Some of this can be accounted for by the higher density of mercaptoethanol 
    molecules in the head group / tail region. There are nearly 40 \% more mercaptoethanol
    molecules than ethylene glycol molecules beyond 0.8 nm from the pore center. 
%    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
%    monomer head group simultaneously,
%    \item Less frequent hydrogen bonding and an affinity for the pore region may be
%    responsible for these hops.
  \end{itemize}

@@

  \noindent 2,3-Dimercapto-1-propanol exhibits slower transport than glycerol because it spends more time
  near monomer head groups. % BJC: should I give all the solutes nicknames (i.e. their residue names)?
  \begin{itemize}
    \item Glycerol frequently hydrogen bonds with more than one head group at a time.
    % BJC: can probably quantify the following:
    \item It also hydrogen bonds with water molecules which increases its stability
    in the pore region.
    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups 
    so it gravitates towards the head group region.
  \end{itemize}

  \noindent DMSO has a comparable MSD to acetone even though its molecular weight is
  about 25 \% larger.
  \begin{itemize}
  	\item The pyramidal structure of DMSO may force it to spend more time closer to
  	the pore center.  % BJC: might be a good place for a numbers comparison
  	\item There are 20 \% more acetone than DMSO molecules in the region beyond 
  	0.8 nm from the pore center.  % based on actual number, not density
  	\item DMSO cannot as easily work its way in and out of the dense head group region. % BJC: some kind of average regional lifetime
  	\item There is a peak in DMSO's radial density near 1.1 nm which may be a consequence of 
  	solute molecules that get stuck in the tails.
  \end{itemize}

@@

  \subsection*{Transport of Ions} % probably just sodium

  Sodium ions coordinate with water molecules.

%  Sodium ions also exhibit hop diffusion because polarized water and
%  carboxylate head groups both work to neutralize its charge.
%  \begin{itemize}
%	\item Ions get trapped in oxygen 'cages' composed of combinations
%	of water molecules, carboxylate head groups and ether oxygens connecting
%	the head groups to their tails.
%  	\item Interesting coordination number data
%	\item Dwell time proportional to surrounding charge within coordination shell
%  \end{itemize}

@@

  Water content affects pore size and strongly influence the MSD of both solutes and
  water. Experiments to understand how controllable this parameter is could be useful.

  Monomers that cannot hydrogen bond. % Hard to make a monomer like this

  Separate polar molecules by creating monomers with head group components designed to
  hydrogen bond.
  \begin{itemize}
  	\item Hbond donors
	\item More incentive to dwell on walls.
  \end{itemize}

@@

  We can use this intuition in order to modify our monomers for a specific 
  separation.
  \begin{itemize}
	\item Increase number of h-bond sites to increase selectivity towards water 
	over polar molecules
  \end{itemize}
